Application of Generalized Additive Models for long-term and seasonal trend analysis of water quality: South San Francisco Bay case study

### 2020-05-29 manu_draft.Rmd
table added for model performance

data(locs)

@@

@@

>>>>

data(locs)
data(modprf)

@@

Table \@ref(tab:modprftab)

@@

```{r modprftab, tab.cap = "Model performance statistics for each station and GAM structure (Table \\@ref(tab:modsumtab)).  Four GAMs were fit to each station and performance is summarized as $\\Delta$ AIC (from `gam0`), GCV, and R-squared values.  Models with the lowest AIC, GCV and highest R-squared values for each station are emphasized."}
totab <- modprf %>% 
  group_by(station) %>% 
  mutate(
    AIC = AIC - max(AIC),
    minaic = AIC == min(AIC), 
    mingcv = GCV == min(GCV),
    maxr2 = R2 == max(R2)
  ) %>% 
  ungroup

boldaic <- as.numeric(rownames(totab)[totab$minaic])
boldgcv <- as.numeric(rownames(totab)[totab$mingcv])
boldr2 <- as.numeric(rownames(totab)[totab$maxr2])

totab <- totab %>% 
  select(-minaic, -mingcv, -maxr2) %>% 
  mutate(
    station = ifelse(duplicated(station), '', station)
  )

tab <- flextable(totab) %>% 
  set_header_labels(
    station = 'Station', 
    model = 'GAM', 
    AIC = 'Delta AIC',
    R2 = 'R-squared'
  ) %>% 
  colformat_num(j = 3, digits = 1) %>%
  colformat_num(j = c(4, 5), digits = 2) %>% 
  bold(i = boldaic, j = 'AIC') %>% 
  bold(i = boldgcv, j = 'GCV') %>% 
  bold(i = boldr2, j = 'R2') %>% 
  border_remove() %>% 
  hline_top(border = fp_border(color = 'black')) %>% 
  font(fontname = 'Times', part = 'all') %>%
  font(j = 2, fontname = 'Consolas') %>% 
  fontsize(size = 12, part = 'all') %>% 
  autofit()

tab
```
